Supplementary Materials for: Empowering the use of community driven preprints in ecology and evolution

### 2024-03-16 supp/supp.qmd
chaneg layout of map

# Load packages
#install.packages("pacman")
pacman::p_load(tidyverse, here, patchwork, readxl, googlesheets4, janitor, maps, forcats,RColorBrewer, flextable)

@@

# Now we can plot the map, but before we do we need to make sure the names in the countries file match those in the region of the world map
  world_map <- map_data(map = "world")

@@

ggplot(countries) +
  geom_map(aes(map_id = country, fill = valid_percent), map = world_map) +
  geom_polygon(data = world_map, aes(x = long, y = lat, group = group), colour = 'black', fill = NA) +
  expand_limits(x = world_map$long, y = world_map$lat) +
  theme_void() +
  coord_fixed() + labs(fill="%")

>>>>

# Load packages
#install.packages("pacman")
pacman::p_load(tidyverse, here, patchwork, readxl, googlesheets4, janitor, maps, forcats,RColorBrewer, flextable, ggimage, gt, performance, ggthemes, mapproj)

@@

# Now we can plot the map, but before we do we need to make sure the names in the countries file match those in the region of the world map
  world_map <- map_data(map = "world") %>% 
  filter(! long > 180)

@@

ggplot(countries) +
  geom_map(aes(map_id = country, fill = valid_percent), map = world_map) +
  geom_polygon(data = world_map, aes(x = long, y = lat, group = group), colour = 'black', fill = NA) +
  expand_limits(x = world_map$long, y = world_map$lat) +
  theme_void() + expand_limits(x = world_map$long, y = world_map$lat) +
  coord_fixed() + labs(fill="%") + theme_map(base_size = 22) + coord_map("moll")
